---
title: "Recommenderlab tutorial"
author: "Wison Hang"
date: "2020/3/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Recommender system example 

```{r echo=TRUE, message=FALSE, warning=FALSE,fig.width=12,fig.height=4}
library(recommenderlab)
library(dplyr)
m <- matrix(sample(c(as.numeric(0:5), NA),50,replace=TRUE, prob=c(rep(.4/6,6),.6)), 
            ncol=10,
            dimnames=list(user=paste("u", 1:5, sep=''),item=paste("i", 1:10, sep='')))
r<- as(m, "realRatingMatrix")

getRatingMatrix(r)

as(r,'list')

head(as(r,'data.frame'))

r_m=normalize(r)

getRatingMatrix(r_m)

image(r, main = "Raw Ratings")
image(r_m, main = "Normalized Ratings")
```

## Inspection of data 
```{r echo=TRUE, message=FALSE, warning=FALSE,fig.width=12,fig.height=6}
data("Jester5k")
Jester5k

r <- sample(Jester5k, 1000)
par(mfrow=c(2,2))
hist(getRatings(normalize(r)), breaks=100)
hist(getRatings(normalize(r, method="Z-score")), breaks=100)
hist(rowCounts(r), breaks=50)
hist(colMeans(r), breaks=20)
```

## Creating a recommender

A recommender is created using the creator functionRecommender().  Available recommendation methods are stored in a registry.  The registry can be queried.  Here we are only interestedin methods for real-valued rating data

```{r echo=TRUE, message=FALSE, warning=FALSE,fig.width=12,fig.height=6}
recommenderRegistry$get_entries(dataType = "realRatingMatrix")

r <- Recommender(Jester5k[1:1000], method = "POPULAR")
names(getModel(r))

getModel(r)$topN
recom <- predict(r, Jester5k[1001:1002], n=5)
recom

#the result contains two ordered top-Nrecommendation lists, one for each user.  The recom-mended items can be inspected as a list.

as(recom, "list")

#Since the top-Nlists are ordered, we can extract sublists of the best items in the top-N.  Forexample, we can get the best 3 recommendations for each list usingbestN().
recom3 <- bestN(recom, n = 3)
as(recom3, "list")

##Many  recommender  algorithms  can  also  predict  ratings.   This  is  also  implemented  usingpredict()with the parametertypeset to"ratings".
recom <- predict(r, Jester5k[1001:1002], type="ratings")
as(recom, "matrix")[,1:10]

recom <- predict(r, Jester5k[1001:1002], type="ratingMatrix")
as(recom, "matrix")[,1:10]

```
## Evaluation of predicted ratings 
```{r echo=TRUE, message=FALSE, warning=FALSE,fig.width=12,fig.height=6}

e <- evaluationScheme(Jester5k[1:1000], method="split", train=0.9,given=15, goodRating=5)
e

## We  create  two  recommenders  (user-based  and  item-based  collaborative  filtering)  using  the training data.
r1 <- Recommender(getData(e, "train"), "UBCF")
r2 <- Recommender(getData(e, "train"), "IBCF")

p1 <- predict(r1, getData(e, "known"), type="ratings")
p2 <- predict(r2, getData(e, "known"), type="ratings")
error<-rbind(
UBCF = calcPredictionAccuracy(p1, getData(e, "unknown")),
IBCF = calcPredictionAccuracy(p2, getData(e, "unknown"))
)
error
```

## Evaluation of a top-N recommender algorithm

```{r  echo=TRUE, message=FALSE, warning=FALSE,fig.width=12,fig.height=6}

scheme <- evaluationScheme(Jester5k[1:1000], method="cross", k=4, given=3,goodRating=5)
scheme

results <- evaluate(scheme, method="POPULAR", type = "topNList",n=c(1,3,5,10,15,20))

getConfusionMatrix(results)[[1]]
avg(results)

##Evaluation results can be plotted usingplot().  The default plot is the ROC curve whichplots the true positive rate (TPR) against the false positive rate (FPR).
par(mfrow=c(1,2))
plot(results, annotate=TRUE)

plot(results, "prec/rec", annotate=TRUE)

##Comparing top-Nrecommendations
algorithms <- list(
  "random items" = list(name="RANDOM", param=NULL),
  "popular items" = list(name="POPULAR", param=NULL),
  "user-based CF" = list(name="UBCF", param=list(nn=50)),
  "item-based CF" = list(name="IBCF", param=list(k=50)),
  "SVD approximation" = list(name="SVD", param=list(k = 50))
  )

results <- evaluate(scheme, algorithms, type = "topNList",n=c(1, 3, 5, 10, 15, 20))

par(mfrow=c(1,2))
plot(results, annotate=c(1,3), legend="bottomright")

plot(results, "prec/rec", annotate=3, legend="topleft")

```

